Predicting trends in the quality of state-of-the-art neural networks without access to training or testing data

### 2021-01-11 submission/resp_to_revs_NatCom.tex
add other comment about confidence bands

\begin{quote}
%(((XXX.  CM: 
%The best thing is to run R2 and Ktau, not p-values, and then also look at the plots.
%I'm open to other suggestions here.
%I'll need to set this up this week, and also create a repo with ALL the plots.
%)))\\
The reviewer is correct.  
We intended for the reader to examine plots to see that the trends are qualitatively in the correct (or incorrect, in some cases for norm-based metrics) direction, and then to look at the numbers to get quantitative insight.
We know that errors are not normal; so, for this and other reasons, in our experience, reporting $p$-values won't clarify the situation.
Instead, to clarify understanding, we have expanded all of the tables that report RMSE and/or $R^2$ to report the Kendal-$\tau$ rank correlation measure; and we have provided figures in the Supplementary Material for all model-dataset pairs, which indicates trends more clearly than the aggregated data.
Also, a point we didn't emphasize enough is that from HT-SR theory we expect that PL-based metrics to have strong linear and not just rank correlation.
We have clarified these points 
in the text 
of the revised manuscript, and in the tables and plots throughout the manuscript.
(Also, additional results beyond what we have in the main text and Supplementary Material are available in our fully-reproducible and publicly-available repo, and it is our hope that that level of transparency will aid the reader's understanding.)
%XXX.  MM STILL TO REFINE THIS ANSWER.
\end{quote}

>>>>

\begin{quote}
%(((XXX.  CM: 
%The best thing is to run R2 and Ktau, not p-values, and then also look at the plots.
%I'm open to other suggestions here.
%I'll need to set this up this week, and also create a repo with ALL the plots.
%)))\\
The reviewer is correct.  
We intended for the reader to examine plots to see that the trends are qualitatively in the correct (or incorrect, in some cases for norm-based metrics) direction, and then to look at the numbers to get quantitative insight.
We know that errors are not normal; so, for this and other reasons, in our experience, reporting $p$-values won't clarify the situation.
Instead, to clarify understanding, we have expanded all of the tables that report RMSE and/or $R^2$ to report the Kendal-$\tau$ rank correlation measure; and we have provided figures in the Supplementary Material for all model-dataset pairs, which indicates trends more clearly than the aggregated data, and which (among other things) show that the plots display the $95\%$ confidence band for every regression along with tabulated results for all metrics.
Also, a point we didn't emphasize enough is that from HT-SR theory we expect that PL-based metrics to have strong linear and not just rank correlation.
We have clarified these points 
in the text 
of the revised manuscript, and in the tables and plots throughout the manuscript.
(Also, additional results beyond what we have in the main text and Supplementary Material are available in our fully-reproducible and publicly-available repo, and it is our hope that that level of transparency will aid the reader's understanding.)
%XXX.  MM STILL TO REFINE THIS ANSWER.
\end{quote}
